Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-15 manuscript/manuscript.Rmd
a bit on constant mortality tuning section

\textbf{The Environment.}
As seen in Fig. **TBD CONCEPTUAL**, we consider four different models of the ecosystem with which the fishery interacts, each of this is called an *environment*, alluding to the environment in an RL setting.
To recap, these four environments are a single-species growth model \eqref{eq:may77} for a harvested species; a three-species model \eqref{eq:3d} with a single harvested species; the same three-species model but with *two* harvested species; and, finally, a three-species model with a time-varying parameter and two harvested species.

@@

\textbf{Training a DRL agent.}
We trained a DRL agent parametrized by a neural network $\theta$ with two hidden, 64-neuron, layers, on a local server with 2 commercial GPUs.
We used the Ray framework\footnote{\url{https://docs.ray.io/}} for training, in particular we used a Ray PPOConfig object to build the algorithm using the default values for all hyper-parameters.
In particular, no hyperparameter tuning was performed.
The agent was trained for 300 iterations of the PPO optimization step.
The total training time was on the order of 30 minutes to 1 hour.

@@

\textbf{Tuning the constant mortality strategy.}
A grid of 100 mortality rates was laid in the interval $[0, 0.5]$.
For each one of these rates, say $M$, we simulated 50 episodes based on \eqref{eq:3d model stoch}:
At each time step the state $(X_t, Y_t, Z_t)$ was observed, a harvest of $MX_t$ was collected and then the system evolved according to its natural dynamics \eqref{eq:3d model stoch}.
The optimal mortality rate was the value $M^*$ for which the mean episode reward was maximal.
We additionally evaluated a more conservative strategy where a mortality of $0.8 M^*$ instead is used.

The result of the tuning procedure is shown in Fig. \ref{fig:tuning}. 
There, we see that the optimal value $M^*$ lies in an area with high episode reward variance.
We will see in Fig. \ref{fig:rew_len_fig} that a likely candidate for this variance is the presence of episodes with early endings.
Thus, the value $0.8 M^*$ supports a smaller variance, and correspondingly -- as Fig. \ref{fig:rew_len_fig} shows -- this policy leads to a much smaller probability of a near-extinction event.

>>>>

\textbf{The Environment.}
As seen in Fig. **TBD CONCEPTUAL**, we consider four different models of the ecosystem with which the fishery interacts, each of this is called an *environment*, alluding to the environment in an RL setting.
To recap, these four environments are a single-species growth model \eqref{eq:may77} for a harvested species; a three-species model \eqref{eq:3d model stoch} with a single harvested species; the same three-species model but with *two* harvested species; and, finally, a three-species model with a time-varying parameter and two harvested species.

@@

\textbf{Training a DRL agent.}
We trained a DRL agent parametrized by a neural network with two hidden, 64-neuron, layers, on a local server with 2 commercial GPUs.
We used the Ray framework\footnote{\url{https://docs.ray.io/}} for training, in particular we used a Ray PPOConfig object to build the algorithm using the default values for all hyper-parameters.
In particular, no hyperparameter tuning was performed.
The agent was trained for 300 iterations of the PPO optimization step.
The total training time was on the order of 30 minutes to 1 hour.

@@

\textbf{Tuning the constant mortality strategy.}
A grid of 101 mortality rates was laid in the interval $[0, 0.5]$ as possible mortality values in the single-fishery cases.
Due to the high memory usage in the two-fishery case, a slightly coarser $51\times51$ grid was set in the square $[0,0.5]^2$ instead.
Since the approach for tuning is completely analogous for all scenarios considered, here we focus on the ‘‘3 species, 1 fishery’’ case.
For each one of these choices of a constant mortality rate, say $M_X$, we simulated 100 episodes based on \eqref{eq:3d model stoch}:
At each time step the state $(X_t, Y_t, Z_t)$ was observed, a harvest of $M_X X_t$ was collected and then the system evolved according to its natural dynamics \eqref{eq:3d model stoch}.
The optimal mortality rate was the value $M_X^*$ for which the mean episode reward was maximal.
The result of the tuning procedure is shown in Fig. \ref{fig:tuning}.
